Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-06-28 introduction.tex
Changing introduction...

The emergence of powerful and inexpensive single-board computers
running full versions of a standard \ac{OS} from many possible in the last
years opens exciting possibilities for researchers. This not only
allows to seamlessly develop implementations that are compatible with
higher end devices and allows the reuse stable software from the Open
Source community. It also enables the deployment and testing of large
scale (hundreds of devices or more) distributed systems at a fraction
of the cost necessary in previous years. This paper focuses on
providing the critical steps and mechanisms followed to deploy, setup,
and maintain a large-scale testbed based on Raspberry Pi devices of
different models. We also complement this with an in-depth evaluation
of the Raspberry Pi as a platform to enable a new paradigm in
networking and storage known as \ac{NC}, which relies on
processing at intermediate nodes to achieve higher throughput, delay
and reliability performance than state-of-the-art routing techniques.

>>>>

% RAW INTRODUCTION: NEED OF DISTRIBUTED NETWORKS AND THE RASPBERRY PI
Due to the advent of the \ac{IoT}, around 50 million devices
ranging from sensors to phones are expected to be connected into
data networks in relatively short period of time \textbf{[REFERENCE]}.
This massive deployment requires the design and testing of new
distributed systems that permit to cope with the amount of traffic
from the proposed services provided by these devices. Therefore,
development platforms that help to quickly deploy, analyze and
evaluate this type of settings are highly desirable for research.
The emergence of a powerful and inexpensive portable computer such
as the Raspberry Pi running standard \ac{OS} like Linux or even
Windows allows to achieve this goal since enables the deployment
of distributed systems at a lower cost than the necessary in
previous years by using standard protocol. We also complement this
with an in-depth evaluation of the Raspberry Pi as a platform to
enable a new paradigm in networking and storage known as \ac{NC},
which relies on processing at intermediate nodes to achieve
higher throughput, delay and reliability performance than
state-of-the-art routing techniques.
